Deep mutational scanning of an H3 hemagglutinin can inform evolutionary forecasting of human H3N2 influenza virus

### 2017-12-05 paper/manuscript.tex
Start integrating figures into manuscript

@@

@@

@@

>>>>

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/dms_overview/dms_overview.pdf}}
\caption{\label{fig:dms_overview}
{\bf Overview of deep mutational scanning experiments of H3 hemagglutinin}
Figure caption text
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/mut_tolerance/entropy_heatmap.pdf}}
\caption{\label{fig:mut_tolerance}
{\bf The mutational tolerance of HA}
Figure caption text
}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/prefslogoplot/rescaled-avgprefs_prefs.pdf}}
\caption{\label{fig:logoplot}
{\bf The site-specific amino-acid preferences of H3 hemagglutinin}
Figure caption text
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/trunkvssidebranch/trunkvssidebranch.pdf}}
\caption{\label{fig:trunkvssidebranch}
{\bf The trunk of a human H3N2 phylogeny has higher mutational effects than those of side branches}
Figure caption text
}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/muteffects_sliding_window/muteffects_sliding_window.pdf}}
\caption{\label{fig:muteffects_sliding_window}
{\bf Sliding window analysis of mutational effects of trunk vs side branches.}
Figure caption text
}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/WSN_trunkvssidebranch/WSN_trunkvssidebranch.pdf}}
\caption{\label{fig:WSN_trunkvssidebranch}
{\bf Trunk vs side branch mutational effects calculated using WSN preferences}
Figure caption text
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/distance_distribution/distance_distribution.pdf}}
\caption{\label{fig:distance_distribution}
{\bf Distribution of preference shifts for protein homologs}
Figure caption text
}
\end{figure}
